Kids Basic Mutual Exclusivity

### 2019-03-01 stats/kids_basic_me.Rmd
update fam picture plot

# length(unique(raw_data$subid))
# 
# d_raw <-raw_data %>%
#   mutate(test_date = as.Date(test_date),
#          experiment = "mcc_kids_inf_2_2",
#          subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))
# 
# log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "inf2")%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# length(unique(log$subid))
# 
# 
# sum(log$keep_drop=="drop")
# 
# d <- left_join(d_raw,log, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"),
#          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
# 
# length(unique(d$subid))

>>>>

# length(unique(raw_data$subid))
# 
d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date))
# 
log <- read_excel("../../../SPIN-subject_log.xlsx", 1)%>%
  filter(Condition == "me")%>%
  select(subid,experimenter,keep_drop,sex,dob)
# 
# length(unique(log$subid))
# 
# 
# sum(log$keep_drop=="drop")
# 
d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
# 
# length(unique(d$subid))
